From DSL to HPC Component Models

### 2015-07-24 WOLFHPC15/article/related.tex
wolfhpc15 24_07

If the study of a DSL dumped to a component assembly has not been studied until now, some component models have already proposed the introduction of time control and data control in the assembly, as for example STCM~\cite{DBLP:confeuropar2008} and Xman~\cite{He12component-baseddesign}. However, both those solutions does not seem to target high performance computing and distributed components.

>>>>

If the study of a DSL dumped to a component assembly has not been studied until now, some component models have already proposed the introduction of time control and data control in the assembly, as for example STCM~\cite{DBLP:confeuropar2008} and XMan~\cite{He12component-baseddesign}. However, both those solutions does not seem to target high performance computing and distributed components.
